Engineering momentum profiles of cold-atom {\color{blue} streams}

### 2019-03-19 Paper/version2/paper.tex
polished abstract

\begin{abstract}
We propose to engineer beams of cold atoms by selecting particles from a trapped gas.
The gas is spatially connected to an external potential whose transmission coefficient allows only
atoms with desired momenta to escape from the trap. We outline an algorithm whose input is the required 
beam profile and output is a filter potential.
A narrow band-pass (NBP) filter transport profile is used as a clear-cut example. 
Further, we discuss a topical application, in which a NBP filter is integrated to produce Bose polarons;
it allows one to study the self-energy and the effective mass of polarons, as well as the corresponding 
Landau criterion.
\end{abstract}

>>>>

\begin{abstract}
We describe a procedure for engineering beams of cold atoms by selectively filtering particles from a trapped gas based on momenta.
A gas is spatially connected to an external potential whose transmission coefficient only allows atoms with desired momenta to escape from the trap. We outline an algorithm whose input is the desired
transmission profile of the outgoing beam and whose output is a filter potential that approximately produces the desired profile.
A narrow band-pass (NBP) filter transport profile is used as a clear-cut example. 
Further, we discuss a topical application, in which a NBP filter is integrated to produce Bose polarons, allowing one to study the self-energy and the effective mass of polarons, as well as the corresponding Landau criterion.
\end{abstract}
